---
title: "Themes, Colors and Extensions"
---


## Themes

HTML documents rendered with Quarto use Bootstrap 5 by default.\
\
Websites/Blogs can use any of the 25 [Bootswatch](https://bootswatch.com) themes included with Quarto. For example, this website uses the cosmo theme. See the 25 themes [here](https://quarto.org/docs/output-formats/html-themes.html) and the .scss theme files are [here](https://github.com/quarto-dev/quarto-cli/tree/main/src/resources/formats/html/bootstrap/themes).\

- You can also [create your own](https://quarto.org/docs/output-formats/html-themes.html#theme-options) themes.\
- [Quickly get your Quarto HTML theme in order - posit::conf(2023)](https://www.youtube.com/watch?v=i2mdxfvm_VY), see `.scss` files [here](https://github.com/gregswinehart/conf-talk-2023/blob/main/theme.scss)


### HTML theme on this website

```{.yaml filename="_quarto.yml"}
format:
  html:
    theme:
      - cosmo
      - theme_custom.scss
    css: styles.css        # empty
    fontsize: 1.1em
    toc: true
```



``` {.scss filename="theme_custom.scss"}
/*-- scss:defaults --*/
// Sass variables for websites, books, manuscripts, revealjs presentations

$navbar-bg: #052962;
```


`yeti` theme could be an alternative. The theme has "Open Sans" font (default).



## Colors

```{r}
library(scales)

my_colors <- c("#1F2F57",  # Volkswagen Space Cadet
               "#6091C3",  # Volkswagen Silver Lake Blue
               "#001E50",  # Volkswagen Navy
               "#041f4a",  # The Guardian Brand Dark
               "#052962",  # The Guardian Brand Main
               "#506991",  # The Guardian Brand Pastel
               "#236925",  # The Guardian Green Dark
               "#3db540",  # The Guardian Green Main
               "#ffffff",  
               "#ffe500",  # The Guardian Highlight main
               "#ffbb50")  # The Guardian Highlight dark

scales::show_col(my_colors, ncol = 3)
```

```{r}
flags01   <- c("#008C45",  # Italy flag
               "#F4F5F0",  # Italy flag     
               "#CD212A",  # Italy flag     
               "#FFFFFF",  # Faroe Islands flag
               "#0165BF",  # Faroe Islands flag     
               "#EE2436",  # Faroe Islands flag                    
               "#078930",  # Ethiopia flag
               "#FCDD09",  # Ethiopia flag     
               "#DA121A",  # Ethiopia flag                    
               "#0F47AF",  # Ethiopia flag
               "#078930",  # Ethiopia flag
               "#FCDD09")  # Ethiopia flag
               
scales::show_col(flags01, ncol = 3)
```

```{r}
flags02   <- c("#0055A4",  # France flag
               "#FFFFFF",  # France flag     
               "#EF4135",  # France flag                      
               "#AA151B",  # Spain flag
               "#F1BF00",  # Spain flag     
               "#AA151B",  # Spain flag    
               "#C60C30",  # Denmark flag
               "#FFFFFF",  # Denmark flag     
               "#C60C30",  # Denmark flag             
               "#004B87",  # Sweden flag
               "#FFCD00",  # Sweden flag     
               "#004B87")  # Sweden flag
               
scales::show_col(flags02, ncol = 3)
```


```{r}
flags03   <- c("#C8102E",  # Norway flag
               "#FFFFFF",  # Norway flag     
               "#003087",  # Norway flag
               "#ffffff",  
               "#ffffff",  
               "#ffffff",  
               "#ffffff",  
               "#ffffff",  
               "#ffffff",  
               "#ffffff",  
               "#ffffff",  
               "#ffffff")

scales::show_col(flags03, ncol = 3)
```


- [A guide to digital design at the Guardian](https://design.theguardian.com/)
- [How to choose your brand colors (plus 10 examples to learn from)](https://www.wix.com/blog/amp/brand-colors)
- [Creating Custom Color Palettes with ggplot2](https://meghan.rbind.io/blog/2022-10-11-creating-custom-color-palettes-with-ggplot2/)




## Extensions

On this website I use the following extensions:

- `quarto-ext/lightbox` , version 0.1.9  
- `quarto-ext/fontawesome` , version 1.2.0
   - {{< fa thumbs-up >}} 
   - {{< fa folder >}}
   - {{< fa chess-pawn >}}
   - {{< fa brands bluetooth >}}
   - {{< fa brands twitter size=2xl >}}
   - {{< fa brands github size=5x >}}
   - {{< fa battery-half size=Huge >}}
   - {{< fa envelope title="An envelope" >}}

See here a [List of Quarto Extensions](https://quarto.org/docs/extensions/).







